Solar wind, F10.7, and geomagnetic activity relationship to the equatorial plasma mass density at geosynchronous orbit

### 2016-09-02 paper/paper.tex
Following meeting with Victoir

The stack plot in the upper panel of Figure \ref{fig:DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991 using data from GOES 6.  The minimum $D_{st}$ median is $-75$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ before and after the event, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.  Error lines for each parameter have a width that is twice the standard deviation of the values used in computing the median divided by the square root of the number of values. For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.

@@

To determine if the magnitude of the density medians in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.  A bootstrap sample of the medians for each epoch day was created by sampling the values used to compute the median on each epoch day with replacement.  The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.

@@

To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts depending whether $B_z$ was above or below its average four hours before and including the onset hour and four hours after and including the hour of onset; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}. Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using a Wilcoxon rank-sum test. For the case where the separation is made according to the value of $B_{z}$ after onset, there is a visible and significant separation between the curves from 7-11 hours after onset, with more negative $B_z$ values corresponding to lower values of $\rho_{eq}$.

@@

Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.  The growth shown here is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 quiet $K_p$ events considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.

@@

Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:HourlyAveragedRhoEvents} depends on $F10.7$.  Statistically significant differences occur independent of whether the separating factor is the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.  Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.  As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower.

>>>>

The stack plot in the upper panel of Figure \ref{fig:DailyAveragedDstEvents} shows the epoch averages for the 75 events from 1989-1991 using data from GOES 6.  The minimum $D_{st}$ median is $-75$~nT.  Consistent with \cite{Takahashi2010}, $D_{st}$ events correspond to elevated $\rho_{eq}$ on the day of the event relative to the day before and after, although the magnitude of increase observed here is $4.5$ amu/cm$^3$ instead of the increase of ${\sim} 10$ amu/cm$^3$ found in Figure 11 of \cite{Takahashi2010}.  The vertical green bars in the $\rho_{eq}$ plot show the number of $\rho_{eq}$ values that were used to compute the medians and red error lines.  The uncertainty is shown with error lines for each parameter that have a width that is twice the standard deviation of the values used in computing the median divided by the square root of the number of values. For the non-$\rho_{eq}$\ parameters, the number of measurements used in computing the medians is typically equal to the number of events, which is much larger than the number of $\rho_{eq}$\ values as all available measurements were used instead of restricting to only values where a $\rho_{eq}$ value also existed.

@@

To determine if the magnitude of the density medians in the top panel of Figure~\ref{fig:DailyAveragedDstEvents} on epoch days -1, 0, and 1 are statistically different from each other, we used a two-population bootstrap test.  A bootstrap sample of the medians for each epoch day was created by sampling all values (with replacement) used to compute the median on each epoch day.  The observed difference between the medians is shown in Table~\ref{BootstrapDifferenceTable} along with the fraction of observations in 1000 bootstrap differences with a different sign than that observed.

@@

To determine if there is an IMF $B_{z}$ dependence, the epoch curves in the bottom panel of Figure~\ref{fig:HourlyAveragedDstEvents} for $\rho_{eq}$ and $B_{z}$ were separated into two parts based on the median value of $B_z$ within a window.  One window covered the four hours before onset and onset and the other covered onset and the following four hours; the result is shown in Figure~\ref{fig:BzBinnedDstEvents}. Any statistically significant difference at a 95\% confidence level between the two parts is indicated by a green dot on the horizontal axis using a Wilcoxon rank-sum test. For the case where the separation is made according to the value of $B_{z}$ after onset, there is a visible and significant separation between the curves from 7-11 hours after onset, with more negative $B_z$ values corresponding to lower values of $\rho_{eq}$.

@@

Figure~\ref{fig:HourlyAveragedRhoEvents} can be compared with Figure~9 of \cite{Denton2016}, which shows daily averages of $\rho_{eq}$ from this dataset after the onset of quiet $K_p$ intervals.  The growth shown here (using the $\rho_m$ threshold criteria with no constraint on $K_p$) is approximately linear and lasts $\sim$ 12--18 hours whereas the 10 $K_p$ events (elevated $K_p$ followed by 2 days with $K_p \le 1^+$) considered by \cite{Denton2016} showed growth that lasted for at least 48~hours.

@@

Figure~\ref{fig:F107Binned} shows how the epoch average curve of $\rho_{eq}$ in Figure~\ref{fig:HourlyAveragedRhoEvents} depends on $F10.7$.  Statistically significant differences occur independent of whether the separating factor is the average of $F10.7$ before or after onset, as expected because the cadence of $F10.7$ is one day and its time scale of variation is longer than that of $\rho_{eq}$.  Events with high $F10.7$ are associated with higher $\rho_{eq}$ before and after event onset but similar peak values.  As was the case for $B_z$, there is an approximately 12--hour time span of linear growth of $\rho_{eq}$ near the time of onset but because the initial starting $\rho_{eq}$ is higher for high $F10.7$, the associated growth rate is lower, consistent with \cite{Denton2016}.
